Model

### 2019-05-29 stats/kids_novelty.Rmd
investigate model parameters
add model predictions for combination

write_csv(d, "../data/child_novelty.csv")

@@

# GLMM

## Models

>>>>

write_csv(d_spin, "../data/child_spin_novelty.csv")
write_csv(d, "../data/child_novelty.csv")
```

@@

# SPIN GLMM

```{r}
spin_model_data <- d_spin%>%
  mutate(age_num = age_num-min(age_num))

spin_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
          data = spin_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

summary(spin_bm)
```

# Comparison with MCC Data

## Model

### 2019-05-29 stats/model.Rmd
add model predictions for combination

sem_know_model <- sem_know_model %>%
  filter(Chain != 3)

@@

# inverse predictions

@@

model_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("GLMM")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")

@@

>>>>

@@

# Inverse predictions

@@

glmm_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("GLMM")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")

@@

```{r}
ggarrange(data_plot,model_plot,glmm_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
```

## Model predictions for combination

```{r}
# novelty data

novel_data <- read_csv("../data/child_spin_novelty.csv")%>%
  mutate(age_num = age_num-min(age_num))

novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
          data = novel_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = F,
          iter = 10000)

summary(novel_bm)

novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
  select(term,Estimate)%>%
  spread(term, Estimate)

comb_model_data_con <- inv_model_data %>%
  mutate(nov_int = novel_params$Intercept,
         nov_slope = novel_params$age_num,
         prior = plogis(nov_int + age * nov_slope),
         alignment = "congruent")

comb_model_data_incon <- inv_model_data %>%
  mutate(nov_int = novel_params$Intercept,
         nov_slope = novel_params$age_num,
         prior = 1- plogis(nov_int + age * nov_slope),
         alignment = "incongruent")

comb_model_data <- bind_rows(
  comb_model_data_con,
  comb_model_data_incon)
```

```{r}
combPred <- '
var allData = dataFromR.data

    var prior = [row.prior, 1-row.prior]

    var modelPredictions = pragmaticListener({label: "novel_word"}, prior, row.speaker_optimality,row.semantic_knowledge)

    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])

```{r predictions pragmatic model ex 3 adults}
comb_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
  data =list(data = comb_model_data),
  data_var = "dataFromR"
)
# 
# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
# 
comb_model_predictions <- comb_model_pred %>%
  separate(`0`, into = c("alignment","item", "age"), sep="/")%>%
  mutate(age = as.numeric(age))%>%
  rename( me_effect = `1`)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num))
```

```{r}
ggplot(comb_model_predictions, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Combination Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  facet_grid(~alignment)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()
```
